intro

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
added references

The postulation of *adaptive* and *maladaptive* ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
Within this framework, *maladaptive*  refers to inflexible ER strategy use or use of strategies that are hindering goal achievement [@Aldao2015] <!--Tamir, M. (2016). Why do people regulate their emotions? A taxonomy of motives in emotion regulation. Personality and Social Psychology Review, 20(3), 199-222. doi:10.1177/1088868315586325 ;  Tamir, M., Bigman, Y. E., Rhodes, E., Salerno, J., & Schreier, J. (2015). An expectancy-value model of emotion regulation: Implications for motivation, emotional experience, and decision making. Emotion, 15(1), 90-103. doi:10.1037/emo0000021  Könnte vor allem das 2. Paper noch hilfreich sein um mehr auf die Values hinzuargumentieren? Ist schon länger her, als ich das gelesen hab. Aber evtl. lohnt es sich, Tamir sagt hier, dass reguliert wird, wenn Personen annehmen, dass die Emotion die sie erzielen möchten, useful ist, also einen Wert hat. Das ist schon anders als die subjective Values, die ihr den ER Strategien zuschreiben möchtet, aber zeigt ja, dass die Analyse von Values im Rahmen von ER als Decision Making schon untersucht wurde, nur eben nicht direkt Values den Strategien zugeschrieben wurde-->.
Adaptive flexible ER requires a large repertoire of ER strategies [@Aldao2015].
The term “repertoire” can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities [@Bonanno2013].
A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology (Dixon-Gordon, Aldao, & De Los Reyes, 2015; Lougheed & Hollenstein, 2012; Southward, Altenburger, Moss, Cregg, & Cheavens, 2018). 
<!-- Dixon-Gordon, K. L., Aldao, A., & De Los Reyes, A. (2015). Repertoires of emotion regulation: A person-centered approach to assessing emotion regulation strategies and links to psychopathology. Cogn Emot, 29(7), 1314-1325. doi:10.1080/02699931.2014.983046
Lougheed, J. P., & Hollenstein, T. (2012). A limited repertoire of emotion regulation strategies is associated with internalizing problems in adolescence. Social Development, 21(4), 704-721. doi:10.1111/j.1467-9507.2012.00663.x
Southward, M. W., Altenburger, E. M., Moss, S. A., Cregg, D. R., & Cheavens, J. S. (2018). Flexible, yet firm: A model of healthy emotion regulation. Journal of Social and Clinical Psychology, 37(4), 231-251. doi:10.1521/jscp.2018.37.4.231-->
Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].

How do people choose strategies from their repertoire? 
Similarly to the expectancy-value model of emotion regulation <!-- Tamir et al, siehe comment oben --> it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made. <!-- Der letzte Teil des Satzes klingt komisch, weiß aber nicht so richtig, was ihr sagen wollt.-->
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging strategies <!-- oder 'of tactics of attentional deployment'?-->, like distraction [@Sheppes2011;@Sheppes2014].
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.<!-- Denise: und fehlen nicht auch noch mehr Studien, die speziell effort im Blick haben? -->
People choose a strategy that they prefer for different, relatively well-known reasons. <!-- Denise: Ist das so? Na gut, es gibt schon einiges an Choice und Goals, aber zu Effort als reason? Ich bin nicht ganz überzeugt davon, dass die Argumentation sich ab hier vor allem auf die nicht gewählte Strategie fokussiert. Kann man nicht auch sagen, dass es noch zu wenig zu effort gibt, das Scheffel2021 eine der ersten war, die mehrere Strategien hinsichtlich effort mit subjektiven, physiologischen und Verhaltensmaßen untersucht hat, dass sich nun die Frage stellt, was genau der subjektive Effort macht, nämlich den Subjective Value beeinflussen, dass dies eben auch für die gewählte Strategie oder im Vergleich mehrerer Taktiken noch nicht untersucht wurde. Und das ihr deshalb nun so vorgeht? -->
However, nothing is revealed about the strategy that is *not chosen*.

>>>>

The postulation of *adaptive* and *maladaptive* ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
Within this framework, *maladaptive*  refers to inflexible ER strategy use or use of strategies that are hindering goal achievement [@Aldao2015] <!--Tamir, M. (2016). Why do people regulate their emotions? A taxonomy of motives in emotion regulation. Personality and Social Psychology Review, 20(3), 199-222. doi:10.1177/1088868315586325 ;  Tamir, M., Bigman, Y. E., Rhodes, E., Salerno, J., & Schreier, J. (2015). An expectancy-value model of emotion regulation: Implications for motivation, emotional experience, and decision making. Emotion, 15(1), 90-103. doi:10.1037/emo0000021  Könnte vor allem das 2. Paper noch hilfreich sein um mehr auf die Values hinzuargumentieren? Ist schon länger her, als ich das gelesen hab. Aber evtl. lohnt es sich, Tamir sagt hier, dass reguliert wird, wenn Personen annehmen, dass die Emotion die sie erzielen möchten, useful ist, also einen Wert hat. Das ist schon anders als die subjective Values, die ihr den ER Strategien zuschreiben möchtet, aber zeigt ja, dass die Analyse von Values im Rahmen von ER als Decision Making schon untersucht wurde, nur eben nicht direkt Values den Strategien zugeschrieben wurde-->.
Adaptive flexible ER requires a large repertoire of ER strategies [@Aldao2015].
The term “repertoire” can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities [@Bonanno2013].
A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology [@DixonGordon2015;@Lougheed2012;@Southward2018]. 
Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].

How do people choose strategies from their repertoire? 
Similarly to the expectancy-value model of emotion regulation <!-- Tamir et al, siehe comment oben --> it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made. <!-- Der letzte Teil des Satzes klingt komisch, weiß aber nicht so richtig, was ihr sagen wollt.-->
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction [@Sheppes2011;@Sheppes2014].
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.<!-- Denise: und fehlen nicht auch noch mehr Studien, die speziell effort im Blick haben? -->
People choose a strategy that they prefer for different, relatively well-known reasons. <!-- Denise: Ist das so? Na gut, es gibt schon einiges an Choice und Goals, aber zu Effort als reason? Ich bin nicht ganz überzeugt davon, dass die Argumentation sich ab hier vor allem auf die nicht gewählte Strategie fokussiert. Kann man nicht auch sagen, dass es noch zu wenig zu effort gibt, das Scheffel2021 eine der ersten war, die mehrere Strategien hinsichtlich effort mit subjektiven, physiologischen und Verhaltensmaßen untersucht hat, dass sich nun die Frage stellt, was genau der subjektive Effort macht, nämlich den Subjective Value beeinflussen, dass dies eben auch für die gewählte Strategie oder im Vergleich mehrerer Taktiken noch nicht untersucht wurde. Und das ihr deshalb nun so vorgeht? -->
However, nothing is revealed about the strategy that is *not chosen*.
